Fourmile Calibrations and Output

### 2025-02-21 fourmile_output_dec2024.Rmd
finished residual plots

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)
library(stringr)

@@

Q 1:1  and residual plots

@@

>>>>

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)
library(stringr)
library(cowplot)

@@

# Q 1:1  and residual plots

@@

################################################################################

# make the actual figures
compFlip <- flowComp %>%
  dplyr::select(-month) %>%
  pivot_longer(!c(date, obs), names_to = 'flow_type',
               values_to = 'flow_cms')

# residual scatter plot
plot <- compFlip %>%
  filter(flow_type %in% c('statn_res', 'grid_res')) %>%
  ggplot(., aes(x=obs, 
                     y=flow_cms,
                color = flow_type)) +
  geom_hline(yintercept = 0, color = "black") +
  geom_point(size=3,
             alpha=0.6) +
  ylim(-5,6) +
  theme_bw(base_size = 20) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(x='Observed discharge (cms)',
       y='Residuals (cms)') +
  facet_wrap(~flow_type,
             labeller = as_labeller(c("grid_res" = "Gridded", "statn_res" = "Station"))) +
  theme(
    legend.position = 'none',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  )

plot

# pick select years to show resids over time
plot_bottom12 <- compFlip %>%
  filter(flow_type %in% c('statn_res', 'grid_res')) %>%
  mutate(year = year(date)) %>%
  filter(year %in% c(2012, 2015, 2017)) %>% 
  mutate(flow_type = if_else(flow_type == 'grid_res', 
                             "Gridded",
                             "Station")) %>%
  ggplot(aes(x = date, y = flow_cms, color = flow_type)) +  
  geom_line(size=1, alpha=0.7) + 
  scale_color_manual(values = c("#0047AB", "orange")) +
  facet_wrap(~year, scales="free_x") +
  labs(x=element_blank(),
       y='Residuals (cms)') +
  theme(
   legend.position = c(0.93, 0.85),
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  )

plot_bottom12

# add 2 above plots together
plot_grid(plot, plot_bottom12, ncol = 1)

# export
ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids.png',
       dpi=600,
       width = 12,
       height = 8)

# OPTION 2 - make the bottom the whole time series
plot_bottom <- compFlip %>%
  filter(flow_type %in% c('statn_res', 'grid_res')) %>%
  complete(date = seq.Date(min(date), max(date), by = "day"), fill = list(flow_cms = NA)) %>%
  # Create a new group ID that resets at each missing value (only where flow_cms is NA)
  mutate(group_id = cumsum(is.na(flow_cms))) %>%
  filter(!is.na(flow_cms)) %>%
  mutate(flow_type = if_else(flow_type == 'grid_res', 
                             "Gridded",
                             "Station")) %>%
  ggplot(aes(x = date, y = flow_cms, color = flow_type, group = group_id)) +  
  geom_line(size=1, alpha=0.7) +  
  ylim(-4,6) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(x=element_blank(),
       y='Residuals (cms)') +
  theme(
    legend.position = c(0.9, 0.87),
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  )

plot_bottom

plot_grid(plot, plot_bottom, ncol = 1)

# export
ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids_option2.png',
       dpi=600,
       width = 12,
       height = 8)
